Price of Anarchy for Mean Field Games

### 2018-08-01 PoA.tex
removed Var assumption Prop 7, reordered cases in prop 7

% proposition b1 and b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming Assumption \ref{assumption}, the initial condition satisfies $Var(\xi)>0$, and:
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2,
	\end{equation*}
	then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	\textbf{Cases 1 and 2:} First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for each $b_1 \leq b_1^*$. Then for each $b_1 \leq b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon},
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$. By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1}  > 1$.\\

	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have:
	$$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty.$$
	Denote $h_u(b_1,t): = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) := B \frac{w_t^{b_1}}{b_1}$. For all $t \in [0,T)$, we have the limits:
	\begin{equation}
		\lim_{b_1 \to \infty} h_u(b_1,t) =  \lim_{b_1 \to \infty} h_w(b_1,t) = 2.
	\label{eq:ut_wt_lim_b1_infty}
	\end{equation}
	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and such that:
	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq 3.$$

@@

	\textbf{Case 4:} Now, consider $\bar{b}_1 \to \infty$.
	Since $A^{u,\bar{b}_1}<0$ and $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have the following limits:
	\begin{equation*}
	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \xrightarrow[\bar{b}_1 \to \infty]{}\infty, \quad -\delta^{-,\bar{b}_1}_u=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u}\xrightarrow[\bar{b}_1 \to \infty]{}0,
	\end{equation*}
	\begin{equation*}
	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} +\frac{\sqrt{\left(b_1+\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1.
	\end{equation*}
	We also have for $t\in [0,T)$:
	$$\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}\leq(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}
	\xrightarrow[\bar{b}_1 \to \infty]{}0,$$
	which implies:
	$
	\lim_{\bar{b}_1\to \infty}\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0.
	$
	Therefore, for $t \in [0,T)$:
	$\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}$. By the same argument, we have for $t \in [0,T)$: $\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}$.

@@

	Now, consider:
	\begin{equation}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
	\label{eq:prop_7_case_4_numerator}
	\end{equation}
	Since $u^{\bar{b}_1}_t$ is decreasing for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$, we have $\bar{b}_1-B u_t^{\bar{b}_1} \geq \bar{b}_1-B u_0^{\bar{b}_1}$. We have the following limits for $t\in[0,T)$:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\bar{b}_1-\delta^{+,\bar{b}_1}_u=-2b_1, \quad \lim_{\bar{b}_1 \to \infty}-\delta^{-,\bar{b}_1}_u\bar{b}_1=BC^u,
	\end{equation*}
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\delta^{+,\bar{b}_1}_u\bar{b}_1e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0, \quad \lim_{\bar{b}_1 \to \infty}(\delta^{-,\bar{b}_1}_u-\bar{b}_1)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0,
	\end{equation*}
	and thus,
	\begin{equation*}
	\begin{split}
	\bar{b}_1-Bu^{\bar{b}_1}_0&=\frac{-BC^u+BD^u(\bar{b}_1-\delta^{+,\bar{b}_1}_u)-\delta^{-,\bar{b}_1}_u\bar{b}_1+(\delta^{+,\bar{b}_1}_u\bar{b}_1+BC^u+BD^u(\delta^{-,\bar{b}_1}_u-\bar{b}_1))e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)T}}{BD^u-\delta^{-,\bar{b}_1}_u+(\delta^{+,\bar{b}_1}_u-BD^u) e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)T}} \\
	&\xrightarrow[\bar{b}_1 \to \infty]{} -2b_1 .
	\end{split}
	\end{equation*}
	Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = -2b_1 < 0$, there exists $\bar{b}_1^{*}\geq\bar{b}_1^{*,lower}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$, $(\bar{b}_1-B u_0^{\bar{b}_1}) \geq -3b_1$. Returning to inequality (\ref{eq:prop_7_case_4_numerator}), and using inequality (\ref{eq:lower_bound_u_w}) we have for $\bar{b}_1 \geq \bar{b}^*_1$:
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}
	\geq \frac{B}{2}\mathbb{E}(\xi)^2 \cdot \frac{1}{4B^2} \cdot \int_{0}^{\frac{T}{2}} e^{2b_1 t + 2(\bar{b}_1 - B u_0^{\bar{b}_1}) t } dt \geq \frac{\mathbb{E}(\xi)^2}{8 B} \int_0^{\frac{T}{2}} e^{-4b_1 t} dt  > 0.
	\end{equation*}
	Therefore,
	$
	\lim_{\bar{b}_1 \to \infty}\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}>0,
	$
	and thus,
	\begin{equation*}
	\begin{split}
	\lim_{\bar{b}_1 \to \infty}\frac{\Delta SC^{\bar{b}_1}}{SC^{MKV,\bar{b}_1}}=\lim_{\bar{b}_1 \to \infty}\frac{\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}}{\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}}=\infty.
	\end{split}
	\end{equation*}
	We conclude
	$
	\lim_{\bar{b}_1 \to \infty} PoA^{\bar{b}_1}=\infty.
	$

>>>>

% proposition b1 and b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming Assumption \ref{assumption}, then:
	\begin{equation*}
	\lim_{b_1 \to \infty} PoA = 1 \qquad \text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{equation*}	
	Furthermore, if:
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2,
	\end{equation*}
	then:
	\begin{equation*}
	    \lim_{b_1 \to 0} PoA > 1\qquad \text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA > 1.
	\end{equation*}
\end{proposition}
\begin{proof}
	\textbf{Case 1:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have:
	$$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty.$$
	Denote $h_u(b_1,t): = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) := B \frac{w_t^{b_1}}{b_1}$. For all $t \in [0,T)$, we have the limits:
	\begin{equation}
		\lim_{b_1 \to \infty} h_u(b_1,t) =  \lim_{b_1 \to \infty} h_w(b_1,t) = 2.
	\label{eq:ut_wt_lim_b1_infty}
	\end{equation}
	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and such that:
	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq 3.$$

@@

	\textbf{Case 2:} Now, consider $\bar{b}_1 \to \infty$.
	Since $A^{u,\bar{b}_1}<0$ and $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have the following limits:
	\begin{equation*}
	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \xrightarrow[\bar{b}_1 \to \infty]{}\infty, \quad -\delta^{-,\bar{b}_1}_u=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u}\xrightarrow[\bar{b}_1 \to \infty]{}0,
	\end{equation*}
	\begin{equation*}
	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} +\frac{\sqrt{\left(b_1+\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1.
	\end{equation*}
	We also have for $t\in [0,T)$:
	$$\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}\leq(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}
	\xrightarrow[\bar{b}_1 \to \infty]{}0,$$
	which implies:
	$
	\lim_{\bar{b}_1\to \infty}\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0.
	$
	Therefore, for $t \in [0,T)$:
	$\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}$. By the same argument, we have for $t \in [0,T)$: $\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}$.

@@

	Now, consider:
	\begin{equation}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
	\label{eq:prop_7_case_4_numerator}
	\end{equation}
	Since $u^{\bar{b}_1}_t$ is decreasing for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$, we have $\bar{b}_1-B u_t^{\bar{b}_1} \geq \bar{b}_1-B u_0^{\bar{b}_1}$. We have the following limits for $t\in[0,T)$:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\bar{b}_1-\delta^{+,\bar{b}_1}_u=-2b_1, \quad \lim_{\bar{b}_1 \to \infty}-\delta^{-,\bar{b}_1}_u\bar{b}_1=BC^u,
	\end{equation*}
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\delta^{+,\bar{b}_1}_u\bar{b}_1e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0, \quad \lim_{\bar{b}_1 \to \infty}(\delta^{-,\bar{b}_1}_u-\bar{b}_1)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0,
	\end{equation*}
	and thus,
	\begin{equation*}
	\begin{split}
	\bar{b}_1-Bu^{\bar{b}_1}_0&=\frac{-BC^u+BD^u(\bar{b}_1-\delta^{+,\bar{b}_1}_u)-\delta^{-,\bar{b}_1}_u\bar{b}_1+(\delta^{+,\bar{b}_1}_u\bar{b}_1+BC^u+BD^u(\delta^{-,\bar{b}_1}_u-\bar{b}_1))e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)T}}{BD^u-\delta^{-,\bar{b}_1}_u+(\delta^{+,\bar{b}_1}_u-BD^u) e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)T}} \\
	&\xrightarrow[\bar{b}_1 \to \infty]{} -2b_1 .
	\end{split}
	\end{equation*}
	Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = -2b_1 < 0$, there exists $\bar{b}_1^{*}\geq\bar{b}_1^{*,lower}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$, $(\bar{b}_1-B u_0^{\bar{b}_1}) \geq -3b_1$. Returning to inequality (\ref{eq:prop_7_case_4_numerator}), and using inequality (\ref{eq:lower_bound_u_w}) we have for $\bar{b}_1 \geq \bar{b}^*_1$:
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}
	\geq \frac{B}{2}\mathbb{E}(\xi)^2 \cdot \frac{1}{4B^2} \cdot \int_{0}^{\frac{T}{2}} e^{2b_1 t + 2(\bar{b}_1 - B u_0^{\bar{b}_1}) t } dt \geq \frac{\mathbb{E}(\xi)^2}{8 B} \int_0^{\frac{T}{2}} e^{-4b_1 t} dt  > 0.
	\end{equation*}
	Therefore,
	$
	\lim_{\bar{b}_1 \to \infty}\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}>0,
	$
	and thus,
	\begin{equation*}
	\begin{split}
	\lim_{\bar{b}_1 \to \infty}\frac{\Delta SC^{\bar{b}_1}}{SC^{MKV,\bar{b}_1}}=\lim_{\bar{b}_1 \to \infty}\frac{\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}}{\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}}=\infty.
	\end{split}
	\end{equation*}
	We conclude $\lim_{\bar{b}_1 \to \infty} PoA^{\bar{b}_1}=\infty.$\\

	\textbf{Cases 3 and 4:} First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for each $b_1 \leq b_1^*$. Then for each $b_1 \leq b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
	\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
	\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon},
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$. By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
	Therefore, $\lim_{b_1 \to 0} PoA^{b_1} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1}  > 1$.
\end{proof}
